DiffScoreModel

### 2023-03-01 DiffScoreModel.Rmd
Updated bias metrics, updated names

abcd_brainage_diff_model <- xgboost::xgb.load(readRDS("xgboost_abcd_diff_brain_age_mod"))

@@

#think I need to now run model on validation set??
abcd_brain_age_correction_diff <-
  abcd_brainage_diff_model %>%
  predict(new_data = df_validation_diff) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = df_validation_baseline$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)

@@

# extract intercept and slope
#abcd_bias_mod_diffcoefficients[["(Intercept)"]]
abcd_bias_intercept_diff <- 
#abcd_bias_mod_diff$coefficients[["truth"]]
abcd_bias_slope_diff <-

@@

save(brain_age_df_diff, file="ABCDBaselineBrainAge.Rda")
save(brain_age_corrected_df_diff, file="ABCDBaselineBrainAgeCorrected.Rda")

>>>>

#abcd_brainage_diff_model <- xgboost::xgb.load(readRDS("xgboost_abcd_diff_brain_age_mod"))

abcd_brainage_diff_model <- readRDS("xgboost_abcd_diff_brain_age_mod_updated.rds")

#https://stackoverflow.com/questions/73506085/old-json-xgboost-model-format-will-be-discontinued-in-version-2-3-warning

@@

#think I need to now run model on validation set??
abcd_brain_age_correction_diff <-
  abcd_brainage_diff_model %>%
  predict(new_data = df_validation_diff) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = df_validation_diff$age_midpoint
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)

@@

# extract intercept and slope
#abcd_bias_mod_diff$coefficients[["(Intercept)"]]
abcd_bias_intercept_diff <- 9.582399
#abcd_bias_mod_diff$coefficients[["truth"]]
abcd_bias_slope_diff <-  0.1240839

@@

save(brain_age_df_diff, file="ABCDBrainAgeDiff.Rda")
save(brain_age_corrected_df_diff, file="ABCDBrainAgeDiffCorrected.Rda")
